Camellia:

### 2012-10-25 docs/Nate/Proposal/presentation/tst_2012_talk.tex

\date{TST Meeting\\ October 17, 2012}
\author[Nate Roberts]{Nate Roberts \\
Collaborators: Leszek Demkowicz, Jesse Chan, Truman Ellis
}
\institute{Institute for Computational and Engineering Sciences\\
The University of Texas at Austin}
\title[Camellia: A DPG Toolbox]{Camellia:}
\subtitle{A Toolbox for a Class of Discontinuous Petrov-Galerkin Methods\\ Using Trilinos}
\begin{document}
\begin{frame}
%\begin{center}
%\includegraphics[width=.8\linewidth]{grand_logo}\\
%\end{center}
\titlepage
%\begin{flushright}
%\includegraphics[scale=0.1]{asc_logo}\\
%\end{flushright}
\end{frame}

@@

%===============================================================================
% From Strong-Form PDE to DPG Form
%===============================================================================
\begin{frame}                                                                                                                                                                          
\frametitle{From Strong-Form PDE to DPG Form}
\begin{center}
\includegraphics[width=\linewidth]{../figures/DPGFormCartoon}\\
\end{center}
\end{frame}              
%===============================================================================
% Solving with DPG
%===============================================================================
\begin{frame}                                                                                                                                                                          
\frametitle{Solving with DPG}
\begin{center} 
\includegraphics[width=0.9\linewidth]{../figures/DPGSolveCartoonNew}\\
\end{center}
\end{frame}

\begin{frame}
\frametitle{Key Features of DPG}\small
\begin{itemize}
\item \pecosbold{guarantees} minimum residual in a norm that depends on the test space, \pecosbold{a free choice}
\item for non-singularly-perturbed, well-posed linear problems, \pecosbold{provably optimal} convergence rates when the ``adjoint graph norm'' is used for the test space
\item \pecosbold{SPD} stiffness matrix
\item discontinuous test space $\implies$ solving for test functions is a \pecosbold{local} operation
\item nonlinear problems: so far, apply the linear method to the linearized problem
\item have also derived a method that instead minimizes the nonlinear residual
\end{itemize}
\begin{block}{Adjoint Graph Norm}
For a strong operator $A$ with formal adjoint $A^{*}$, the \pecosbold{adjoint graph norm} on the test space $V$ is given by
\[
\NVRnorm{v}_{\rm graph} = \NVRnorm{v}_{H_{A^{*}}} = \left( \NVRnorm{v}^{2} + \NVRnorm{A^{*}v}^{2}\right)^{1/2}.
\]
\end{block}
\end{frame}

@@

  VarPtr psi_hat_n = varFactory.fluxVar("\\widehat{\\phi}_n");
  VarPtr phi_hat = varFactory.traceVar("\\widehat{\\psi}");
  VarPtr psi = varFactory.fieldVar("\\psi", VECTOR_L2);
  VarPtr phi = varFactory.fieldVar("\\phi", L2);
\end{lstlisting}

>>>>

\date{TST Meeting\\ October 17, 2012}
\author[Nate Roberts]{Nate Roberts \\
Collaborators: Leszek Demkowicz, Jesse Chan, Truman Ellis
}
\institute{Institute for Computational and Engineering Sciences\\
The University of Texas at Austin}
\title[Camellia: A DPG Toolbox]{Camellia:}
\subtitle{A Toolbox for a Class of Discontinuous Petrov-Galerkin Methods\\ Using Trilinos}
\begin{document}

%PATTER: I'm a PhD. candidate in the computational science, engineering, and mathematics program here at UT.
\begin{frame}
\begin{center}
\includegraphics[width=.6\linewidth]{grand_logo}\\
\end{center}
\titlepage
%\begin{flushright}
%\includegraphics[scale=0.1]{asc_logo}\\
%\end{flushright}
\end{frame}

@@

%===============================================================================
% From Strong-Form PDE to DPG Form
%===============================================================================
\begin{frame}                                                                                                                                                                          
\frametitle{From Strong-Form PDE to DPG Form}
\begin{center}
\includegraphics[width=\linewidth]{../figures/DPGFormCartoon}\\
\end{center}
\end{frame}              
%===============================================================================
% Solving with DPG
%===============================================================================
%\begin{frame}                                                                                                                                                                          
%\frametitle{Solving with DPG}
%\begin{center} 
%\includegraphics[width=0.9\linewidth]{../figures/DPGSolveCartoonNew}\\
%\end{center}
%\end{frame}

\begin{frame}                                                                                                                                                                          
\frametitle{Solving with DPG}
\begin{itemize}
\item We drive \pecosbold{adaptivity} using an energy norm in which we can precisely determine the error:
\[
\NVRnorm{u-u_{h}}_{E} = \NVRnorm{R_{V}^{-1}\left(Bu_{h} - l \right)}_{V}.
\]
\item In practice, must \pecosbold{approximate} $R_{V}^{-1}$.  We do this by using ``enriched'' test space $V_{p+\Delta p}$.  ($\Delta p=$ 1 or 2, usually.)
\item Test functions belong to a \pecosbold{broken} (element-wise conforming) space.
\item \pecosbold{Discontinuous} test space $\implies$ optimal test functions can be determined element-locally.
\item The system matrix is symmetric-positive definite:
\[
K_{ij} = b(e_{i}, v_{e_{j}}) = (v_{e_{i}}, v_{e_{j}})_{V} = (v_{e_{j}}, v_{e_{i}})_{V} = b(e_{j}, v_{e_{i}}) = K_{ji}
\]
\end{itemize}

\begin{frame}
\frametitle{Key Features of DPG}\small
\begin{itemize}
\item \pecosbold{guarantees} minimum residual in a norm that depends on the test space, \pecosbold{a free choice}
\item for non-singularly-perturbed, well-posed linear problems, \pecosbold{provably optimal} convergence rates when the ``adjoint graph norm'' is used for the test space
%\item \pecosbold{SPD} stiffness matrix
\item nonlinear problems: so far, apply the linear method to the linearized problem
\item have also derived a method that instead minimizes the nonlinear residual
\end{itemize}
\begin{block}{Adjoint Graph Norm}
For a strong operator $A$ with formal adjoint $A^{*}$, the \pecosbold{adjoint graph norm} on the test space $V$ is given by
\[
\NVRnorm{v}_{\rm graph} = \NVRnorm{v}_{H_{A^{*}}} = \left( \NVRnorm{v}^{2} + \NVRnorm{A^{*}v}^{2}\right)^{1/2}.
\]
\end{block}
\end{frame}

@@

  VarPtr psi_hat_n = varFactory.fluxVar("\\widehat{\\psi}_n");
  VarPtr phi_hat = varFactory.traceVar("\\widehat{\\phi}");
  VarPtr psi = varFactory.fieldVar("\\psi", VECTOR_L2);
  VarPtr phi = varFactory.fieldVar("\\phi", L2);
\end{lstlisting}
